---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# MovieShots

<!-- badges: start -->
[![R build status](https://github.com/jmelican21/MovieShots/workflows/R-CMD-check/badge.svg)](https://github.com/jmelican21/MovieShots/actions)
<!-- badges: end -->

The goal of MovieShots is to provide information on shot duration in movies. The data spans 192 movies across the century from 1915 to 2015. 

## Installation

You can install MovieShots from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jmelican21/MovieShots")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example, message=FALSE, warning=FALSE}
library(MovieShots)
library(tidyverse)

meandur <- MovieShots %>% group_by(year) %>% summarize(mean = mean(duration))


runtime <- MovieShots %>% group_by(year,title) %>% summarize(runtime = sum(duration)/60) #divide by 60 for minutes

```


### a. How has average shot duration changed over time?

SOLUTION:

```{r message = FALSE, warning = FALSE}
ggplot(meandur,
  aes(x = year, y = mean)) +
 geom_col() + geom_smooth(se= FALSE, color = "red")+
labs(x = "Release Year", y = "Average shot duration (seconds)")
```

As shown above, the average shot duration of movies in this dataset peaks in 1945 at over 12 seconds before declining fairly steadily since the 1960's to around 3 seconds in 2015.




### b) Has total runtime changed over the past century?

SOLUTION:

```{r message = FALSE, warning = FALSE}
ggplot(runtime,
  aes(x = year, y = runtime)) +
  geom_point() + 
  geom_smooth(se = FALSE) + 
  labs(x = "Release Year", y = "Runtime (minutes)")
```

After increasing throughout the first half of the 20th century, average runtime has remained fairly constant at about 120 minutes since the 1960's. 

